s.function

### 2025-02-02 src/la_RF_corrected.Rmd
all lad + oa without the hold-out

detectCores()
cl <- makePSOCKcluster(14)
registerDoParallel(cl)

start.time <- Sys.time()
model.all <- train(n ~                                                          # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df,# %>% filter(year > 1999),                         # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE       
#   2     variance    0.02811777  0.8509273  0.01912432
#   2     extratrees  0.02782836  0.8508316  0.01901921
#   4     variance    0.02867344  0.8466191  0.01970102
#   4     extratrees  0.02795250  0.8509000  0.01911956
#   6     variance    0.02974784  0.8364575  0.02066007
#   6     extratrees  0.02830277  0.8482189  0.01944133
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees and min.node.size = 5.

@@

#(8 is the number of tuning parameter, mtry for rf, here equal to ncol(iris)-2)
set.seed(831)
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 8) # 6 feature + 2

@@

# detectCores()
cl <- makePSOCKcluster(14)
registerDoParallel(cl)

@@

  model.all <- train(n ~                                                        # REPLACE n WITH growth
                       #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                       #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                       n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist,
                   data = df %>% filter(RGN21CD!=i), #& year > 1999),           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  assign(paste0("model.all",as.character(i)), model.all) # object name = region not in the training data
}

stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 4 minutes 
```

@@

detectCores()
cl <- makePSOCKcluster(14)
registerDoParallel(cl)

start.time <- Sys.time()
model.all <- train(growth ~                                                     # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df %>% filter(year > 1999),                           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2658416  0.5284505  0.1934243
#   2     extratrees  0.2612133  0.5292689  0.1900297
#   4     variance    0.2621564  0.5194092  0.1912807
#   4     extratrees  0.2611575  0.5183202  0.1910029
#   6     variance    0.2609983  0.5140347  0.1891971
#   6     extratrees  0.2607463  0.5124544  0.1907650
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 6, splitrule = extratrees and min.node.size = 5.

@@

  model.all <- train(growth ~                                                   # REPLACE n WITH growth
                       #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                       #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                       n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist,
                   data = df %>% filter(RGN21CD!=i & year > 1999),              # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  assign(paste0("model.all",as.character(i)), model.all) # object name = region not in the training data
}

stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 3 minutes 
```

>>>>

# detectCores()
# cl <- makePSOCKcluster(14)
# registerDoParallel(cl)

start.time <- Sys.time()
model.all <- train(n ~                                                          # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df,# %>% filter(year > 1999),                         # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 5082, 4354, 4650, 4746, 5130, 4928, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE       
#   2     variance    0.02899374  0.8242687  0.02021469
#   2     extratrees  0.02919421  0.8158094  0.02039216
#   4     variance    0.02929606  0.8252793  0.02067827
#   4     extratrees  0.02922286  0.8194044  0.02056084
#   6     variance    0.03068719  0.8155331  0.02189821
#   6     extratrees  0.02938456  0.8190111  0.02074402
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and min.node.size = 5.

@@

#(8 is the number of tuning parameter, mtry for rf, here equal to ncol(iris)-2)
set.seed(831)
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 6) # 6 feature + 2

@@

# detectCores()
# cl <- makePSOCKcluster(14)
# registerDoParallel(cl)

@@

  model.all <- train(n ~                                                        # REPLACE n WITH growth
                       #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                       #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                       n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist,
                   data = df %>% filter(RGN21CD!=i), #& year > 1999),           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)
  assign(paste0("model.all",as.character(i)), model.all) # object name = region not in the training data
}

# stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 4 minutes 
```

@@

# detectCores()
# cl <- makePSOCKcluster(14)
# registerDoParallel(cl)

start.time <- Sys.time()
model.all <- train(growth ~                                                     # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df %>% filter(year > 1999),                           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4356, 3421, 3720, 4068, 4104, 3872, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2894270  0.5199902  0.2268798
#   2     extratrees  0.2872946  0.5173582  0.2238973
#   4     variance    0.2883168  0.5049246  0.2257499
#   4     extratrees  0.2860372  0.5056609  0.2225991
#   6     variance    0.2921377  0.4901490  0.2284739
#   6     extratrees  0.2861368  0.4945032  0.2219559
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 4, splitrule = extratrees and min.node.size = 5.

@@

  model.all <- train(growth ~                                                   # REPLACE n WITH growth
                       #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                       #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                       n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist,
                   data = df %>% filter(RGN21CD!=i & year > 1999),              # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)
  assign(paste0("model.all",as.character(i)), model.all) # object name = region not in the training data
}

# stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 3 minutes 
```

### 2025-02-02 src/la_RF_corrected_10.Rmd
all lad + oa without the hold-out

start.time <- Sys.time()
model.all <- train(n ~                                                          # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df,# %>% filter(year > 1999),                         # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.1877289  0.7762104  0.1222690
#   2     extratrees  0.1945882  0.7537303  0.1274455
#   4     variance    0.1899769  0.7754308  0.1253349
#   4     extratrees  0.1925299  0.7604062  0.1270665
#   6     variance    0.1926697  0.7707287  0.1277624
#   6     extratrees  0.1930151  0.7601929  0.1280934
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and min.node.size = 5.

@@

  model.all <- train(n ~                                                        # REPLACE n WITH growth
                       #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                       #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                       n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist,
                   data = df %>% filter(RGN21CD!=i), #& year > 1999),           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  assign(paste0("model.all",as.character(i)), model.all) # object name = region not in the training data
}

# stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 4 minutes 
```

@@

detectCores()
cl <- makePSOCKcluster(14)
registerDoParallel(cl)

start.time <- Sys.time()
model.all <- train(growth ~                                                     # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df %>% filter(year > 1999),                           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2773784  0.6171406  0.2025901
#   2     extratrees  0.2696423  0.6424804  0.1985126
#   4     variance    0.2834811  0.5991036  0.2058774
#   4     extratrees  0.2720828  0.6324695  0.2007287
#   6     variance    0.2902072  0.5801010  0.2101899
#   6     extratrees  0.2755322  0.6215775  0.2037045
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees and min.node.size = 5.

@@

# detectCores()
cl <- makePSOCKcluster(14)
registerDoParallel(cl)

>>>>

start.time <- Sys.time()
model.all <- train(n ~                                                          # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df,# %>% filter(year > 1999),                         # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 5082, 4354, 4650, 4746, 5130, 4928, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.1908100  0.7375479  0.1279762
#   2     extratrees  0.1994918  0.7045691  0.1340791
#   4     variance    0.1899064  0.7491920  0.1294553
#   4     extratrees  0.1985176  0.7110348  0.1347026
#   6     variance    0.1911215  0.7530296  0.1312026
#   6     extratrees  0.1992530  0.7110950  0.1359168
# 
# Tuning parameter 'min.node.size' was held constant at
#  a value of 5
# RMSE was used to select the optimal model using
#  the smallest value.
# The final values used for the model were mtry =
#  4, splitrule = variance and min.node.size = 5.

@@

  model.all <- train(n ~                                                        # REPLACE n WITH growth
                       #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + n.nearest.city + year,
                       #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                       n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist,
                   data = df %>% filter(RGN21CD!=i), #& year > 1999),           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)
  assign(paste0("model.all",as.character(i)), model.all) # object name = region not in the training data
}

# stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 18 minutes 
```

@@

start.time <- Sys.time()
model.all <- train(growth ~                                                     # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df %>% filter(year > 1999),                           # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4356, 3421, 3720, 4068, 4104, 3872, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.3044927  0.5868676  0.2369061
#   2     extratrees  0.2954167  0.6153847  0.2312128
#   4     variance    0.3170846  0.5455342  0.2439098
#   4     extratrees  0.3008763  0.5922954  0.2347268
#   6     variance    0.3222021  0.5224533  0.2464477
#   6     extratrees  0.3055270  0.5782538  0.2388544
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees and min.node.size = 5.

@@

### 2025-02-02 src/s_la_per_firm_corrected.Rmd
all lad + oa without the hold-out

# xmid = 2003.118
xmid.uk <- tidy(fit) %>% 
  filter(term=="xmid") %>% 
  dplyr::select(estimate) %>% as.numeric()

@@

```{r}
a.la <- tibble()
all.la <- df %>% 
  filter(ladcd != "NA") %>% 
  distinct(ladcd) %>% 
  #slice_head(n=100) %>% 
  simplify2array()

@@

ggplot(pred %>% 
              left_join(a.la), 
            aes(x = year, y = n, color = fast, group = ladcd)) +
  geom_line(aes(y = prednls), size = .1, alpha = .7) +
  scale_x_continuous(NULL, labels = as.character(df$year), breaks = df$year) +
  #geom_vline(xintercept = xmid.uk) +
  ylab("N. of websites / per firm") + 
  labs(color = "Website diffusion speed") +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"),
                     limits = force) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank(),
        legend.position = "bottom") +
  geom_vline(aes(xintercept = xmid.uk, linetype="dashed"), colour="grey30") +
  scale_linetype_manual(values=c("dashed"), 
                        labels = c(""), 
                        name = unname(TeX(c("$t_{0}$ for the UK"))))

>>>>

# xmid.uk = 2003.118
xmid.uk <- tidy(fit) %>% 
  filter(term=="xmid") %>% 
  dplyr::select(estimate) %>% as.numeric()

@@

```{r}
# xmid.uk = 2003.118

a.la <- tibble()
all.la <- df %>% 
  filter(ladcd != "NA") %>% 
  distinct(ladcd) %>% 
  #slice_head(n=100) %>% 
  simplify2array()

@@

ggplot(pred %>% 
              left_join(a.la), 
            aes(x = year, y = n, color = fast, group = ladcd)) +
  geom_line(aes(y = prednls), size = .1, alpha = .7) +
  scale_x_continuous(NULL, labels = as.character(df$year), breaks = df$year) +
  #geom_vline(xintercept = xmid.uk) +
  ylab("N. of websites per firm") + 
  labs(color = "Website diffusion speed") +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"),
                     limits = force) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank(),
        legend.position = "bottom") +
  geom_vline(aes(xintercept = xmid.uk, linetype="dashed"), colour="grey30") +
  scale_linetype_manual(values=c("dashed"), 
                        labels = c(""), 
                        name = unname(TeX(c("$t_{0}$ for the UK"))))
